### 2013-12-17 poster_new/conference_poster_4.tex
results change

\headerbox{RESULTS}{name=results,column=1,below=metrics}{

Hierarchical architecture reduces communication overhead (Figure \ref{fig:msg}) by an order of magnitude while compromising modestly on optimality: shortest path length (17.4\%) (Figure \ref{fig:path}) and minimum maximum link utilization (12.8\%) (Figure \ref{fig:util}).
}

>>>>

\headerbox{RESULTS}{name=results,column=1,below=metrics}{
    \begin{itemize}
        \item Reduces communication overhead by TODO (Figure \ref{fig:msg})
        \item Increases shortest path length by 17.4\% (Figure \ref{fig:path})
        \item Increases minimum maximum link utilization by 12.8\% (Figure \ref{fig:util}).
    \end{itemize}
Hierarchical architecture reduces communication overhead by an order of magnitude while compromising modestly on optimality
}
